Making Sequential Programs Deterministic

### 2019-04-06 design.tex
design edits

\<OrderNonDet> may only be written on collections and maps.
A map is a dictionary or an associative array, such as a hash table.
\OurTypeSystem largely treats a map as a collection of key--value pairs.
Both collections and maps may be \<Det>, \<OrderNonDet>, or \<NonDet>, and
the element types can be specified independently of the collection type,
including their qualifiers.

@@

\todo{Can we come up with more examples of interesting functions to
  describe here?  Or put them in section 3.}

@@

\todo{I feel that this section is very confusing.}

@@

More specifically, rule \rulename{set precision} of
\cref{fig-precision-rules} expresses that the return type of \<equals()>
is \<Det> if both arguments have type \<OrderNonDet Set> and neither argument
has {@code List} or a subtype within its type argument.
Without this rule, the type would be \<NonDet> which is sound but imprecise.

>>>>

\<OrderNonDet> may only be written on collections and maps.
A map is a dictionary or an associative array, such as a hash table.
\OurTypeSystem largely treats a map as a collection of key--value pairs.
Both collections and maps may be \<Det>, \<OrderNonDet>, or \<NonDet>.
The basetypes of their elements can be specified independently of the collection basetypes.
However, an element type qualifier must be a subtype of the collection type qualifier.
The next section discusses type well-formedness in detail.
%and
%the element types can be specified independently of the collection type,
%including their qualifiers.

@@

%\todo{Can we come up with more examples of interesting functions to
%  describe here?  Or put them in section 3.}

@@

%\todo{I feel that this section is very confusing.}

@@

More specifically, rule \rulename{set precision} of
\cref{fig-precision-rules} expresses that the return type of \<equals()>
is \<Det> if both arguments have type \<OrderNonDet Set> and neither argument
has \code{@OrderNonDet List} or a subtype within its type argument.
Without this rule, the type would be \<NonDet> which is sound but imprecise.
